The Hydrogen Epoch of Reionization Array (HERA)

### 2015-08-12 orig_hera_concept.tex
renamed tex files to new versions --> active one is manuscript.tex

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for the following class files: copernicus.cls, copernicus2.cls, copernicus_discussions.cls
%% The class files, the Copernicus LaTeX Manual with detailed explanations regarding the comments
%% and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Publication Production Office (production@copernicus.org).
%% http://publications.copernicus.org

%% Differing commands regarding the specific class files are highlighted.

%% copernicus.cls
\documentclass[ars]{copernicus}

%% copernicus2.cls
%\documentclass[journal abbreviation]{/Users/daviddeboer1/Documents/Papers/Copernicus_LaTeX_Package_v_2_7/copernicus2}

%% copernicus_discussions.cls
%\documentclass[ars, hvmath, online]{/Users/daviddeboer1/Documents/Papers/Copernicus_LaTeX_Package_v_2_7/copernicus_discussions}
\usepackage{amsmath}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\nwnh{{\sl NWNH}}

\newcommand{\simgt}{\stackrel{>}{_{\sim}}}
\newcommand{\mnras}{Month. Not. Royal Astron. Soc.}
\newcommand{\apj}{Astrophys. J.}
\newcommand{\apjl}{Astrophys. J. Lett.}
\newcommand{\pasa}{Proc. Astron. Soc. Aust.}
\newcommand{\pasp}{Proc. Astron. Soc. Pac.}
\newcommand{\aj}{Astron. J.}
\newcommand{\prd}{Uknown}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\k{{\bf k}}
\def\sky{{\theta}}
\def\HI{{H{\small I }}}
\def\HII{{H{\small II }}}
\def\xHI{{x_{\rm\HI}}}
\def\arcdeg{{$^o$}}
\def\arcmin{{$''$}}
\begin{document}

@@

\begin{abstract}
The Donald C. Backer Hydrogen Epoch of Reionization Array (HERA) is a staged
experiment that uses the unique properties of the 21-cm line from neutral
hydrogen to probe the Epoch of Reionization (EoR) and the preceding Dark
Ages. During these epochs, roughly 0.3-1 Gyr after the Big Bang, the first
stars and black holes heat and reionize the Universe following cosmic
recombination. Direct observation of the large scale structure of
reionization and its evolution with time will have
a profound impact on our understanding of the birth of the first galaxies
and black holes, their influence on the intergalactic medium (IGM), and
cosmology.  HERA is a compact hexagonal-packed array of 14-meter paraboloids 
operating from 50 - 225 MHz.
\end{abstract}

\introduction  %% \introduction[modified heading if necessary]
\label{sec:intro}
The Donald C. Backer Hydrogen Epoch of Reionization Array (HERA) is a staged project
that uses the unique properties of the 21-cm line of neutral hydrogen to probe the
Epoch of Reionization (EoR) and the preceding Dark Ages. During these epochs, roughly
0.3-1 Gyr after the Big Bang, the first stars and black holes heated and reionized
the Universe, which at that time existed as a nearly uniform sea of warm neutral
hydrogen.  Figure \ref{fig:theUniverse} is a cartoon showing cosmic evolution from the Big Bang on the left through
to HERA today. The period of cosmic reionization represents one of the few global
phase changes in the evolution of the Universe.
Direct observation of the large scale structure of reionization and its
evolution with time will have a profound impact on our understanding of the birth of
the first galaxies and black holes, their influence on the intergalactic medium
(IGM), and cosmology.

Detecting, characterizing and ultimately imaging this epoch is a key goal in
furthering our understanding of the Universe and was the top priority in the Radio,
Millimeter, and Sub-millimeter category of recommended new facilities in the most
recent decadal survey of astronomical priorities (\ref{NWNH}). Current projects
(PAPER, MWA, LOFAR, GMRT YYYYYGIVE REFSYYYYY) are striving to make the first detection of the statistical
power spectrum of the signal, but current best limits still fall above even
optimistic predictions of its intrinsic strength. While these projects are still
taking data, it is recognized that an optimized array based on our new understanding
of the signal characteristics is needed to make a strong detection and begin to
characterize this signal over multiple scales and redshifts.

The HERA roadmap is a phased set of experiments that build on its predecessors and preceding stages.
The first phase of the HERA roadmap entailed the operation of the
PAPER and MWA telescopes to explore techniques and designs required to
detect the primordial HI signal in the presence of radio continuum
foreground emission some four orders of magnitude brighter. Studies
with PAPER and the MWA have led to a new understanding of the
interplay of foreground and instrumental systematics in the context of
a three-dimensional cosmological intensity-mapping experiment.  YYYYYGIVE REFSYYYYY 
We are
now able to remove foregrounds to the limits of our sensitivity with
these instruments, culminating in the first physically meaningful
upper limits on the power spectrum of 21~cm emission from
reionization (see Fig \ref{fig:eor_pspec}).

Building on this understanding, the next stage of HERA incorporates a new
14m diameter antenna element that is optimized both for sensitivity
and for minimizing foreground systematics.  Arranging these elements
in a compact hexagonal grid yields an array that facilitates
calibration, leverages proven foreground removal techniques, and is
scalable to large collecting areas. The array will be located near the current PAPER
experiment
in the radio quiet environment of the SKA site in Karoo, South Africa,
and will have a sensitivity close to two orders of magnitude better than
PAPER and the MWA.  HERA's sensitivity coupled with broader frequency coverage, 
will enable HERA to paint an
uninterrupted picture through reionization, back to the end of the
Dark Ages.  As an array, it can be used in smaller arrays along the way to 
achieve timely science.  Two benchmarks are planned:

@@

%\appendix
%\section{\\ \\ \hspace*{-7mm} HEADING}    %% Appendix A
%And everything nice.
%\subsection                               %% Appendix A1, A2, etc.
%And everything else.

@@

\bibliographystyle{copernicus}
\bibliography{biblio}

%\begin{thebibliography}{}
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 1
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 2
%
%...
%
%\end{thebibliography}

%% Literature citations
%% command                        & example result
%% \citet{jones90}|               & Jones et al.\ (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[ht]
\vspace*{2mm}
\begin{center}
\includegraphics[width=\textwidth]{plots/herauniall.png}
\end{center}
\caption{\small Cartoon showing the development of the Universe and HERA's observing window into it (dashed lines).  The blue solid
line shows the \HI transition frequency as a function of redshift/cosmic evolution age.  The black dashed lines indicate the HERA EOR ``core'' band and blue dashed lines the expanded band, which are detailed in Table \ref{tab:heraband}.}
\label{fig:theUniverse}
\end{figure*}

\begin{figure}[t]\centering
\includegraphics[width=\columnwidth]{plots/eor_pspec_2014.png}
\includegraphics[width=\columnwidth]{plots/hera_pk3pk.png}
\caption{\small Top: HERA's power-spectrum sensitivity (solid)
relative to a fiducial ionization model (dotted line; $\xHI=0.37$, $z=9.0$).  
Sensitivities reflect staged array size and
improving analysis software that expands the range
of modes free of foreground systematics. 
Bottom: The current best upper limit on the 21~cm reionization power spectrum,
obtained with a 32-element PAPER deployment \citep{parsons_et_al2013}.  These upper limits
constrain the brightness temperature of the IGM at $z\sim8$, showing
a departure from adiabatic cooling presumed to be indicative of X-ray heating.
}\label{fig:eor_pspec}
\end{figure}

\begin{figure}[t]
\vspace*{2mm}
\begin{center}
\includegraphics[width=\columnwidth]{plots/heraXY.png}
\end{center}
\caption{Scaling  \label{fig:heraXY}}
\end{figure}

\begin{figure}[t]
\vspace*{2mm}
\begin{center}
\includegraphics[width=\columnwidth]{plots/costing.png}
\end{center}
\caption{Costing  \label{fig:costing}}
\end{figure}

\begin{figure}[t]
    \centering
        \includegraphics[height=1.5in]{plots/new_antenna_closeup.jpg}
        \includegraphics[height=1.5in]{plots/Engineering/recv_node.png}
        \includegraphics[height=1.5in]{plots/Engineering/digital.png}
    \caption{-0.1in}{0.99}{-0.1in}{\small
    Existing components re-used in the HERA design include:
    the PAPER dipole antenna (left), 
    receivers in a node module (center), and
    the 128-element correlator deployed in the Karoo (right).
}\label{fig:components}
\end{figure}

@@

\begin{figure}[t]
\vspace*{2mm}
\begin{center}
\includegraphics[width=12cm]{plots/HERA_high_level_block_diagram.png}
\end{center}
\caption{System  \label{fig:systemOverview}}
\end{figure}

\begin{figure}[t]
\vspace*{2mm}
\begin{center}
\includegraphics[width=12cm]{plots/config.png}
\end{center}
\caption{Configuration  \label{fig:config}}
\end{figure}

%f
%\begin{figure*}[t]
%\vspace*{2mm}
%\begin{center}
%\includegraphics[width=12cm]{FILE NAME}
%\end{center}
%\caption{TEXT}
%\end{figure*}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[t]
\caption{HERA band in frequency, redshift, cosmic age and comoving distance.}
\label{tab:heraband}
\vskip4mm
\centering
\begin{tabular}{| c | c | c | c |} \hline
\textbf{Frequency [MHz]} & \textbf{Redshift} & \textbf{Age} & \textbf{Look-back} \\
\textbf{[MHz]}                   &                            & \textbf{[Myr]}  & \textbf{[Gly]} \\ \hline
50 & 27.4    & 164 & 13.6 \\ \hline
100 & 13.2  & 372 & 13.4 \\ \hline
200  & 6.1    & 960  & 12.8 \\ \hline
225  &  5.3   & 1,135  &  12.7 \\ \hline
\end{tabular}
\end{table*}

@@

%t
%\begin{table}[t]
%\caption{TEXT}
%\vskip4mm
%\centering
%\begin{tabular}{column = lcr}
%\tophline

%\middlehline

%\bottomhline
%\end{tabular}
%\end{table}
\begin{table*}[t]
\small
 \centering
 \begin{tabular}{c||r||r|r} 
%\begin{deluxetable}{c||r||r|r}
%\tabletypesize{\small}
%\tablecaption{\small
\hline
%\startdata
Instrument & Collecting Area (m$^2$) & Foreground avoidance & Foreground modeling \\
\hline
PAPER & 528 & 1.93 & 8.86 \\
MWA & 896 & 2.46 & 6.40 \\
LOFAR NL Core & 35,762 & 2.76 & 17.37 \\
\textbf{HERA-127} & \textbf{19,500} & \textbf{10.88} & \textbf{35.65} \\
\textbf{HERA-331} & \textbf{50,900} & \textbf{25.44} & \textbf{87.20} \\
SKA1 Low Core & 833,190 & 97.92 & 284.85 \\
%\enddata
\end{tabular}
\caption{Power spectrum signal-to-noise (``number of sigmas") at $z=9.5$ for various instruments, adapted from \citet{pober_et_al2014}.  By leveraging a filled, redundant configuration of dishes with high collecting area, HERA-331 allows high-significance power spectrum measurements using current foreground avoidance techniques, with further enhancements possible with likely advances in foreground modeling.}
\label{tab:signif}
\end{table*}

Print this is some text in between.

\begin{table*}[t]
\small
%\begin{center}
% \begin{deluxetable}{lcc}
% \tabletypesize{\small}
% \tablecaption{HERA-331 basic parameters.}
% \tablehead{\colhead{Parameter} & \colhead{Design} & \colhead{Performance at 150 MHz}}
%    \startdata
\begin{tabular}{l | c | c} \hline
Parameter & Design & Performance\\  \hline
    Element diameter / FoV & 14 m & 9\arcdeg \\ 
    %Total collecting area & 54186 m$^2$ \\
    Min baseline length / largest scale & 14.6 m & 7.8\arcdeg \\
    Max core baseline length / synthesized beam & 306.6 m & 24\arcmin \\ 
    Max outrigger baseline length  & 1066.5 m & 9\arcmin \\
    Frequency / redshift range  & 50 - 250 MHz digitized \\
    & 70 - 230 MHz useable & 19.2 - 5.2 \\ 
    & 100 MHz correlated & \\
    Spectral channel width & 97.7 kHz & \\    
    System temperature / sensitivity & $100 + 120 (\nu/\rm{150~MHz})^{-2.55}$ K 
    & 50 $\mu \rm{Jy}~\rm{beam}^{-1}~\sqrt{\rm{hour}}$ \\
    \hline
%     At 150 MHz ($z=8.5$): & \\
%     ~{   }Naturally weighted synthesized beam FWHM & $24\arcmin$ \\
%     ~{   }Uniformly weighted synthesized beam FWHM & $9\arcmin$ \\
%     ~{   }Field of view FWHM & 9\arcdeg \\
%     ~{   }Point source RMS & 50 $\mu$Jy in 100 hrs \\
%  \enddata
%    \hline
 %\end{deluxetable}
\end{tabular}
\caption{HERA-331 basic parameters.  Design parameters are connected to the derived instrument performance at 150 MHz.}
\label{tab:BasicParameters}
\vspace{.2in}
%\end{deluxetable}
%\end{center}
\end{table*}

%\end{deluxetable}

%% TWO-COLUMN TABLE

%t
%\begin{table*}[t]
%\caption{TEXT}
%\vskip4mm
%\centering
%\begin{tabular}{column = lcr}
%\tophline

%\middlehline

%\bottomhline
%\end{tabular}
%\end{table*}

%% The different columns must be seperated with a & command and should
%% end with \\ to identify the column brake.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% If figures and tables must be numbered 1a, 1b, etc. the following command
%% should be inserted before the begin{} command.

%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}

>>>>

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

\documentclass[ars]{copernicus}

%\usepackage{amsmath}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\nwnh{{\sl NWNH}}

\newcommand{\simgt}{\stackrel{>}{_{\sim}}}
\newcommand{\mnras}{Month. Not. Royal Astron. Soc.}
\newcommand{\apj}{Astrophys. J.}
\newcommand{\apjl}{Astrophys. J. Lett.}
\newcommand{\pasa}{Proc. Astron. Soc. Aust.}
\newcommand{\pasp}{Proc. Astron. Soc. Pac.}
\newcommand{\aj}{Astron. J.}
\newcommand{\prd}{Unknown}
\def\eg{{\em e.g.~}}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\k{{\bf k}}
\def\sky{{\theta}}
\def\HI{{H{\small I }}}
\def\HII{{H{\small II }}}
\def\xHI{{x_{\rm\HI}}}
\def\arcdeg{{$^o$}}
\def\arcmin{{$''$}}

\begin{document}

@@

\begin{abstract}
Hydrogen Epoch of Reionization Array  is a staged
experiment that uses the unique properties of the 21-cm line from neutral
hydrogen to probe the Epoch of Reionization (EoR) and the preceding Dark
Ages. During these epochs, roughly 0.3-1 Gyr after the Big Bang, the first
stars and black holes heat and reionize the Universe following cosmic
recombination. Direct observation of the large scale structure of
reionization and its evolution with time will have
a profound impact on our understanding of the birth of the first galaxies
and black holes, their influence on the intergalactic medium (IGM), and
cosmology.  The current stage under development and described in this paper is a compact hexagonal-packed array of 352 14-meter paraboloids 
operating from about 70 - 220 MHz.
\end{abstract}

\introduction  %% \introduction[modified heading if necessary]
\label{sec:intro}
The Hydrogen Epoch of Reionization Array roadmap (HERA Roadmap) is a staged project
that uses the unique properties of the 21-cm line of neutral hydrogen to probe the
Epoch of Reionization (EoR) and the preceding Dark Ages. During these epochs, roughly
0.3-1 Gyr after the Big Bang, the first stars and black holes heated and reionized
the Universe, which at that time existed as a nearly uniform sea of warm neutral
hydrogen.  Figure \ref{fig:theUniverse} is a cartoon showing cosmic evolution from the Big Bang on the left through
to HERA today. The period of cosmic reionization represents one of the few global
phase changes in the evolution of the Universe.
Direct observation of the large scale structure of reionization and its
evolution with time will have a profound impact on our understanding of the birth of
the first galaxies and black holes, their influence on the intergalactic medium
(IGM), and cosmology.

Detecting, characterizing and ultimately imaging this epoch is a key goal in
furthering our understanding of the Universe and was the top priority in the Radio,
Millimeter, and Sub-millimeter category of recommended new facilities in the most
recent Decadal Survey of Astronomy and Astrophysics \citet{NWNH}. Current projects
(PAPER \citep{2014ApJ...788..106P}, 
MWA, \citep{2013PASA...30....7T},
LOFAR \citep{2013A&A...550A.136Y}, 
GMRT \citep{2011MNRAS.413.1174P}) are striving to make the first detection of the statistical
power spectrum of the signal, but current best limits still fall above even
optimistic predictions of its intrinsic strength. While these projects are still
taking data, it is recognized that an optimized array based on our new understanding
of the signal characteristics is needed to make a strong detection and begin to
characterize this signal over multiple scales and redshifts.

The HERA Roadmap is a phased set of experiments that build on its predecessors and preceding stages.
The first phase of the HERA roadmap entailed the operation of the
PAPER and MWA telescopes to explore techniques and designs required to
detect the primordial HI signal in the presence of radio continuum
foreground emission some four orders of magnitude brighter. Studies
with PAPER and the MWA have led to a new understanding of the
interplay of foreground and instrumental systematics in the context of
a three-dimensional cosmological intensity-mapping experiment.  YYYYYGIVE REFSYYYYY 
We are
now able to remove foregrounds to the limits of our sensitivity with
these instruments, culminating in the first physically meaningful
upper limits on the power spectrum of 21~cm emission from
reionization (see Fig \ref{fig:eor_pspec}).

Building on this understanding, the next stage called the Donald C. Backer Hydrogen Epoch of Reionization Array (HERA) incorporates a new
14m diameter antenna element that is optimized both for sensitivity
and for minimizing foreground systematics.  Arranging these elements
in a compact hexagonal grid yields an array that facilitates
calibration, leverages proven foreground removal techniques, and is
scalable to large collecting areas. The array will be located near the current PAPER
experiment
in the radio quiet environment of the SKA site in Karoo, South Africa,
and will have a sensitivity close to two orders of magnitude better than
PAPER and the MWA.  HERA's sensitivity coupled with broader frequency coverage, 
will enable HERA to paint an
uninterrupted picture through reionization, back to the end of the
Dark Ages.  As an array, it can be used in smaller arrays along the way to 
achieve timely science.  Two benchmarks are planned:

@@

%\appendix
%\section{}    %% Appendix A
%\subsection{}                               %% Appendix A1, A2, etc.

@@

%% REFERENCES

\bibliographystyle{copernicus}
\bibliography{biblio}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% ONE-COLUMN FIGURES

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{plots/herauniall.png}
\caption{\small Cartoon showing the development of the Universe and HERA's observing window into it (dashed lines).  The blue solid
line shows the \HI transition frequency as a function of redshift/cosmic evolution age.  The black dashed lines indicate the HERA EOR ``core'' band and blue dashed lines the expanded band, which are detailed in Table \ref{tab:heraband}.}
\label{fig:theUniverse}
\end{figure}

\begin{figure}[t]
\includegraphics[width=4.1cm]{plots/eor_pspec_2014.png}
\includegraphics[width=4.1cm]{plots/hera_pk3pk.png}
\caption{\small Top: HERA's power-spectrum sensitivity (solid)
relative to a fiducial ionization model (dotted line; $\xHI=0.37$, $z=9.0$).  
Sensitivities reflect staged array size and
improving analysis software that expands the range
of modes free of foreground systematics. 
Bottom: The current best upper limit on the 21~cm reionization power spectrum,
obtained with a 32-element PAPER deployment \citep{parsons_et_al2013}.  These upper limits
constrain the brightness temperature of the IGM at $z\sim8$, showing
a departure from adiabatic cooling presumed to be indicative of X-ray heating.}
\label{fig:eor_pspec}
\end{figure}

\begin{figure}[t]
\includegraphics[width=8.3cm]{plots/heraXY.png}
\caption{\small Scaling}
\label{fig:heraXY}
\end{figure}

\begin{figure}[t]
\includegraphics[width=8.3cm]{plots/costing.png}
\caption{Costing}
\label{fig:costing}
\end{figure}

\begin{figure}[t]
        \includegraphics[width=2.7cm]{plots/new_antenna_closeup.jpg}
        \includegraphics[width=2.7cm]{plots/recv_node.png}
        \includegraphics[width=2.7cm]{plots/digital.png}
    \caption{\small
    Existing components re-used in the HERA design include:
    the PAPER dipole antenna (left), 
    receivers in a node module (center), and
    the 128-element correlator deployed in the Karoo (right).}
\label{fig:components}
\end{figure}

@@

%f
\begin{figure*}[t]
\includegraphics[width=12cm]{plots/HERA_high_level_block_diagram.png}
\caption{System}
\label{fig:systemOverview}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{plots/config.png}
\caption{Configuration}
\label{fig:config}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[t]
\caption{HERA band in frequency, redshift, cosmic age and comoving distance.}
\label{tab:heraband}
\vskip4mm
\centering
\begin{tabular}{| c | c | c | c |} \hline
\textbf{Frequency [MHz]} & \textbf{Redshift} & \textbf{Age} & \textbf{Look-back} \\
\textbf{[MHz]}                   &                            & \textbf{[Myr]}  & \textbf{[Gly]} \\ \hline
50 & 27.4    & 164 & 13.6 \\ \hline
100 & 13.2  & 372 & 13.4 \\ \hline
200  & 6.1    & 960  & 12.8 \\ \hline
225  &  5.3   & 1,135  &  12.7 \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[t]
\small
 \centering
 \begin{tabular}{c||r||r|r} 
%\begin{deluxetable}{c||r||r|r}
%\tabletypesize{\small}
%\tablecaption{\small
\hline
%\startdata
Instrument & Collecting Area (m$^2$) & Foreground avoidance & Foreground modeling \\
\hline
PAPER & 528 & 1.93 & 8.86 \\
MWA & 896 & 2.46 & 6.40 \\
LOFAR NL Core & 35,762 & 2.76 & 17.37 \\
\textbf{HERA-127} & \textbf{19,500} & \textbf{10.88} & \textbf{35.65} \\
\textbf{HERA-331} & \textbf{50,900} & \textbf{25.44} & \textbf{87.20} \\
SKA1 Low Core & 833,190 & 97.92 & 284.85 \\
%\enddata
\end{tabular}
\caption{Power spectrum signal-to-noise (``number of sigmas") at $z=9.5$ for various instruments, adapted from \citet{pober_et_al2014}.  By leveraging a filled, redundant configuration of dishes with high collecting area, HERA-331 allows high-significance power spectrum measurements using current foreground avoidance techniques, with further enhancements possible with likely advances in foreground modeling.}
\label{tab:signif}
\end{table*}

\begin{table*}[t]
\begin{tabular}{l | c | c} \hline
Parameter & Design & Performance\\  \hline
    Element diameter / FoV & 14 m & 9\arcdeg \\ 
    %Total collecting area & 54186 m$^2$ \\
    Min baseline length / largest scale & 14.6 m & 7.8\arcdeg \\
    Max core baseline length / synthesized beam & 306.6 m & 24\arcmin \\ 
    Max outrigger baseline length  & 1066.5 m & 9\arcmin \\
    Frequency / redshift range  & 50 - 250 MHz digitized \\
    & 70 - 230 MHz useable & 19.2 - 5.2 \\ 
    & 100 MHz correlated & \\
    Spectral channel width & 97.7 kHz & \\    
    System temperature / sensitivity & $100 + 120 (\nu/\rm{150~MHz})^{-2.55}$ K 
    & 50 $\mu \rm{Jy}~\rm{beam}^{-1}~\sqrt{\rm{hour}}$ \\
    \hline
%     At 150 MHz ($z=8.5$): & \\
%     ~{   }Naturally weighted synthesized beam FWHM & $24\arcmin$ \\
%     ~{   }Uniformly weighted synthesized beam FWHM & $9\arcmin$ \\
%     ~{   }Field of view FWHM & 9\arcdeg \\
%     ~{   }Point source RMS & 50 $\mu$Jy in 100 hrs \\
\end{tabular}
\caption{HERA-331 basic parameters.  Design parameters are connected to the derived instrument performance at 150 MHz.}
\label{tab:BasicParameters}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TABLES
%%
%% The different columns must be seperated with a & command and should
%% end with \\ to identify the column brake.

@@

%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}

%% NUMBERING OF FIGURES AND TABLES
%%
%% If figures and tables must be numbered 1a, 1b, etc. the following command
%% should be inserted before the begin{} command.
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}

%% MATHEMATICAL EXPRESSIONS

%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%
%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%% Vectors are identified in bold italic font using \vec{x}
%% Matrices are identified in bold roman font
%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%% The character * should not be applied as mutliplication sign
